Contextual Combinatorial Cascading Bandits

### 2016-01-08 contextual combinatorial cascading bandits.tex
update introduction and reference

Combinatorial multi-armed bandit(MAB) problem has been studied extensively in statistics and machine learning.

The cascade model is popular to describe user behaviors in recommendation systems. When recommended with a list of items, such as web pages or advertisements, the user checks from the first item to the last and selects the first attractive item. The items before the selected one are not attractive and the items after the selected one are unobserved. Also in networking routing problem, if we want to check a path from source to end to confirm whether it is blocked, we can just stop checking when meeting a blocked edge. The cascade model is useful to describe such kind of partial-observation problem.

@@

>>>>

A stochastic combinatorial bandit \cite{gai2012combinatorial,chen2013combinatorial} is an online learning problem, where on each round a learning agent chooses a subset of ground items under combinatorial constraints and receives the according reward. When each item is represented by a feature vector that can be observed by the learning agent, the problem is known as contextual combinatorial bandit, which is developed in recommender systems and studied in \cite{qin2014contextual}.

@@

In real applications, the cascade model is popular to describe user behaviors in recommendation systems. When recommended with a list of items, such as web pages or advertisements, the user checks from the first item to the last and selects the first attractive item. The items before the selected one are not attractive and the items after the selected one are unobserved. Also in networking routing problem, if we want to check a path from source to end to confirm whether it is blocked, we can just stop checking when meeting a blocked edge. The cascade model is useful to describe such kind of partial-observation problem.
